msuRACiFits_fits_rice

### 2025-05-28 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Updated fitting script

```{r}
base_path <- here("Outputs", "Parameters")
```

@@

### Calculate Gamma Star at different temperatures using calcGammaStar:

```{r}
msuRACiFit::calcGammaStar(c,dHa,tleaf,oxygen)
```

The tool uses preset in-vitro values from Hermida-Carrera et al (2016), where everything is presented in ppm, except for N. tabacum and A. thaliana.

Since we are analyzing the A/Ci in Pa, we have to adjust the resulting Gamma\*, Kc and Ko that we get in ppm to Pa before running calculations.

$c$ and $\Delta H_a$ for Gamma\* presented in the app/ preset table are for ppm, and gamma\* is corrected as follows:\
\
Gamma\* (Pa) = Gamma\*(ppm) \* 1000 / 1000000 \* Patm,\
Kc (Pa) = Kc(umol mol -1) \* 1000 / 1000000 \* Patm\
Kcair (Pa) = Kcair(umol mol -1) \* 1000 / 1000000 \* Patm,\
Ko (kPa) = O(Pa) / ((Kcair(Pa) / Kc(Pa)) - 1)/1000

@@

### Call calcgammastar function with different temperature inputs and get outputs saved in single vector for 8 files:

@@

### Next, we account for the variation in Press for each dataset and converting GammaStar back to Pa:

@@

```{r}
Gstars_rice_file <- file.path(base_path, "Gstars_rice.csv")
write.csv(Gstars_rice,Gstars_rice_file) #ppm
```

```{r}
Gstars_Pa_rice_file <- file.path(base_path, "Gstars_Pa_rice.csv")
write.csv(Gstars_Pa_rice,Gstars_Pa_rice_file) #Pa
```

@@

#### Calculate Kc and Kcair for our Tleaf values in umol mol-1 then convert them into Pa before working out Ko.

@@

@@

```{r}
all_param$Ko<-(21000 / ((all_param$Kcair / all_param$Kc) - 1))/1000 
all_param$Temperature <- mean_temps 
all_param$Press <- mean_press

all_param_file <- file.path(base_path, "kinetic_parameters_rice.csv")
write.csv(all_param,all_param_file)
```

@@

```{r}
for (o in seq_along(complete_Fits_rice_list)) {
  filename <- sprintf("completeFits_rice_params_%d.csv", o)
  output_filename <- file.path(base_path,filename)
  write.csv(complete_Fits_rice_list[[o]][[1]], 
            file = output_filename, 
            row.names = FALSE)
}
```

@@

### Save data tables:

```{r}
for (p in seq_along(complete_Tables_rice_list)) {
  filename <- sprintf("completeFits_rice_dataTable_%d.csv", p)
  output_filename <- file.path(base_path,filename)
  write.csv(complete_Tables_rice_list[[p]], 
            file = output_filename, 
            row.names = FALSE)
}
```

@@

```{r}
SSR_file <- file.path(base_path, "SSR_values_rice.csv")
write.csv(SSR,SSR_file)
```

@@

```{r}
for (p in seq_along(complete_Graphs_rice_list)) {
  filename <- sprintf("completefits_rice_Graph_%d.png", p)
  output_filename <- file.path(base_path, filename)

@@

```{r}
limitations_file <- file.path(base_path, "completeFit_rice_limitations.csv")
write.csv(limitations_list,limitations_file)
```

>>>>

```{r}
output_path <- here("Outputs", "Parameters")
```

@@

Gamma Star can be calculated for different temperatures using the calcGammaStar function.

msuRACiFit uses preset in-vitro values from Hermida-Carrera et al (2016), where everything is presented in ppm, except for N. tabacum and A. thaliana.

Since the A/Ci responses are analysed in Pa, the resulting Gamma\*, Kc and Ko must be adjusted from ppm to Pa units before running calculations.

$c$ and $\Delta H_a$ for Gamma\* presented in the app/ preset table are for ppm, and Gamma\* is corrected as follows:\
\
Gamma\* (Pa) = Gamma\*(ppm) \* 1000 / 1000000 \* Patm,\
Kc (Pa) = Kc(umol mol -1) \* 1000 / 1000000 \* Patm\
Kcair (Pa) = Kcair(umol mol -1) \* 1000 / 1000000 \* Patm,\
Ko (kPa) = O(Pa) / ((Kcair(Pa) / Kc(Pa)) - 1)/1000

@@

### Call the calcgammastar function with different temperature inputs and get outputs saved in a single vector for 8 files:

@@

### Next, account for the variation in Press for each dataset and converting GammaStar back to Pa:

@@

```{r}
Gstars_rice_file <- file.path(output_path, "Gstars_rice.csv")
write.csv(Gstars_rice,Gstars_rice_file) #ppm
```

```{r}
Gstars_Pa_rice_file <- file.path(output_path, "Gstars_Pa_rice.csv")
write.csv(Gstars_Pa_rice,Gstars_Pa_rice_file) #Pa
```

@@

#### Calculate Kc and Kcair for our Tleaf values in umol mol-1, then convert them into Pa before working out Ko.

@@

### Call the kinetic_params function to calculate $K_{cair}$ in $umol \ mol^{-1}$ :

```{r}
Kcair_umol <- vector("list", length(mean_temps)) 
for (j in seq_along(mean_temps)) { 
    Kcair_umol[[j]] <- kinetic_params(mean_temps[j])[2]}
```

### Save Kcair and temperature values in .csv files:

```{r}
Kcair_file <- file.path(output_path, "Kcair_umol_rice.csv")
temp_file <- file.path(output_path, "temps_rice.csv")

write.csv(Kcair_umol, Kcair_file)
write.csv(mean_temps,temp_file)
```

@@

```{r}
all_param$Ko<-(21000 / ((all_param$Kcair / all_param$Kc) - 1))/1000 
all_param$Temperature <- mean_temps 
all_param$Press <- mean_press
```

### Save parameters in a file:

```{r}
all_param_file <- file.path(output_path, "kinetic_parameters_rice.csv")
write.csv(all_param,all_param_file)
```

@@

```{r}
for (o in seq_along(complete_Fits_rice_list)) {
  filename <- sprintf("completeFits_rice_params_%d.csv", o)
  output_filename <- file.path(output_path,filename)
  write.csv(complete_Fits_rice_list[[o]][[1]], 
            file = output_filename, 
            row.names = FALSE)
}
```

### Calculate $g_{m}$ in $umol \ m^{-2} \ s^{-1}$:

```{r}
gm_umol <- vector("list", length(mean_press)) 
for (j in seq_along(mean_press)) { 
    gm_umol[[j]] <- complete_Fits_rice_list[[j]][[1]]$gm*(mean_press[j]/1000)}
```

### Save gm values in a file:

```{r}
gm_file <- file.path(output_path, "gm_umol_rice.csv")
write.csv(gm_umol,gm_file)
```

@@

### Save data tables in separate files:

```{r}
for (p in seq_along(complete_Tables_rice_list)) {
  filename <- sprintf("completeFits_rice_dataTable_%d.csv", p)
  output_filename <- file.path(output_path,filename)
  write.csv(complete_Tables_rice_list[[p]], 
            file = output_filename, 
            row.names = FALSE)
}
```

### Extract the parameter values from each list and combine them in a single dataframe, adding an identifier column 1-9 (based on k) as the first column:

```{r}
combined_results <- do.call(rbind, 
                            lapply(seq_along(complete_Fits_rice_list), function(k) {
  if(!is.null(complete_Fits_rice_list[[k]][[1]])) {
    df <- complete_Fits_rice_list[[k]][[1]]  
    df$Dataset_ID <- k  
    df <- df[, c("Dataset_ID", 
                 setdiff(names(df), 
                         "Dataset_ID"))]  
    return(df)
  } else {
    return(NULL)
  }
}))
```

### Save combined parameter values:

```{r}
parameters_file <- file.path(output_path, "complete_Fits_rice_params_all.csv")
write.csv(combined_results,parameters_file)
```

@@

```{r}
SSR_file <- file.path(output_path, "SSR_values_rice.csv")
write.csv(SSR,SSR_file)
```

@@

```{r}
for (p in seq_along(complete_Graphs_rice_list)) {
  filename <- sprintf("completefits_rice_Graph_%d.png", p)
  output_filename <- file.path(output_path, filename)

@@

```{r}
limitations_file <- file.path(output_path, "completeFit_rice_limitations.csv")
write.csv(limitations_list,limitations_file)
```
